Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-07-26 Scripts/Initial_Analysis.Rmd
Changed trans_index function to account for noise in two steps, time variation and model variarion

TransIndex <- function(Centroids, # Expecting the results from the GetCentroids function
                       Id, # A numeric value representing a neighbouring interaction (ONE!)
                       Hist_y = 2000,
                       Plot = F){ # The LAST year of Historical data

@@

  # Estimate noice from ensemble members
  historic_sd <- Trans_index %>% 
    filter(year < Hist_y) %>% 
    group_by(taxon_key,neighbour_id,ensemble) %>% #Average historic data per ensemble
    summarise_at(vars("trend"),
                 c(trend= mean)
                 ) %>% 
    group_by(taxon_key,neighbour_id) %>% #Capture ensemble variation
    summarise_at(vars("trend"),
                 c(hist_mean=mean,
                   noise=sd,
                   n_ens = ~n())
                 )

>>>>

TransIndex <- function(Centroids, # Expecting the results from the GetCentroids function
                       Id, # A numeric value representing a neighbouring interaction (ONE!)
                       Hist_y = 2005,
                       Plot = F){ # The LAST year of Historical data

@@

  # Estimate noice from ensemble members
  historic_sd <- Trans_index %>% 
    filter(year <= Hist_y) %>% 
    group_by(taxon_key,neighbour_id,ensemble) %>% #Average historic data per ensemble
    summarise_at(vars("trans_index"),
                 c(trend= mean)
                 ) %>% 
    group_by(taxon_key,neighbour_id) %>% #Capture ensemble variation
    summarise_at(vars("trend"),
                 c(hist_mean=mean,
                   noise=sd,
                   n_ens = ~n())
                 )
